Weakly Nonlinear MRI: Notes

### 2014-04-09 notes/mri_notes.tex
a little more

Which, substituting in the forms of $\mathbf{V_1}$ and $\mathbf{V_2}$ and taking Umurhan+'s $\mathbf{N3}$, gives us the full amplitude equation:\\

@@

I believe one can state this as ``$\mathbb{V}^\dagger$ must be orthogonal to $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$". Because both $\mathbb{V}^\dagger$ and $\mathbb{V}_{11}$ are even symmetric about x = 0, the requirement is really that $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$ is odd symmetric with respect to x, since $\partial_Z \alpha(T, Z)$ is presumably not zero everywhere.

>>>>

Which, substituting in the forms of $\mathbf{V_1}$ and $\mathbf{V_2}$ and taking Umurhan+'s $\mathbf{N_3}$, gives us the full amplitude equation:\\

@@

I believe one can state this as ``$\mathbb{V}^\dagger$ must be orthogonal to $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$". Because both $\mathbb{V}^\dagger$ and $\mathbb{V}_{11}$ are even symmetric about x = 0, the requirement is really that $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$ is odd symmetric with respect to x, since $\partial_Z \alpha(T, Z)$ is presumably not zero everywhere. \\

This solvability condition is enforceable on all terms resonant with $e^{iQz}$. That is why we take the inner product of $\mathbb{V}^\dagger$ with the $e^{iQz}$ terms in the $\mathcal{O}(\epsilon^3)$ equation to arrive at the first amplitude equation (see above). \\

The second solvability condition is found for the terms without $e^{iQz}$ dependence: \\
